Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-30 paper/paper.Rmd
optimize spatial disc section

#### Leave-one-disc-out

@@

Another buffering oriented resampling method is "Leave-one-disc-out" from package \pkg{sperrorest}.
The name originates from the generic "Leave-one-out" method.
More specifically, the 'disc' which is being left our here refers to the radial area of test sets created from this method.

Around the radial test set a buffer zone / neutral area can be defined in which observations are excluded from the training set, increasing the spatial distance between training and test sets.

```{r disc, fig.cap="Visualization of 'Leave-one-disc-out' method.", out.width="50%"}
resampling_disc = rsmp("spcv_disc", folds = 5, radius = 200L, buffer = 300L)
resampling_disc$instantiate(task)

>>>>

#### Leave-one-disc-out --- sperrorest

@@

Another buffering oriented resampling method is "Leave-one-disc-out" from package \pkg{sperrorest}.
The name originates from the generic "Leave-one-out" method.
The 'disc' part in the name here refers to the radial area/buffer zone around the test set which is (optionally) being left out within each fold.

In addition, one can specify to sample with replacement by setting `replace = TRUE`.

The method starts from a randomly selected observation and adds all points within the buffer zone area set via variable `radius` by the user.

Around the radial test set a buffer zone / neutral area can be defined via variable `buffer` in which observations are excluded from the training set, increasing the spatial distance between training and test sets.

```{r disc, fig.cap="Visualization of 'Leave-one-disc-out' method.", out.width="50%"}
resampling_disc = rsmp("spcv_disc", folds = 5, radius = 300L, buffer = 400L)
resampling_disc$instantiate(task)
